---
title: "Georeference_Village_School"
author: "Bihter Erbas"
date: "11/04/2023"
output:
  pdf_document: default
  df_print: paged
  latex_engine: xelatex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
options(tinytex.verbose = TRUE)
rm(list=ls())
library(sf)
library(rgeos)
library(rgdal)
library(dplyr)
library(tidyverse)
library(stringr)
library(readxl)
#library(tmap)
library(writexl)
library(preregr) # to avoid bind_rows problem
library(glue)
library(openxlsx)
library(rstudioapi)
library(here) # Package to access parent directory while reading files (to rerun the code smoothly anywhere)
library(ggplot2)
library(hrbrthemes)
library(kableExtra)

# Set the path current open file
current_path = rstudioapi::getActiveDocumentContext()$path 
setwd(dirname(current_path ))


```

```{r echo=FALSE}
sigeschools.all <- read_excel(paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "raw")),'sigeschools.xlsx', sep="/")) %>% 
  dplyr::mutate_at(.vars=vars(ProvincePoliAdmin), list(~ gsub("-", " ", .))) # Harmonize province name
```

## Bring all schools together

In this part,  I'm binding all the georeferenced data. After removing the duplicates by ceni_site_vote_ID, ceni_nom_sv, latitude there are 4121 distinct georeferenced observations in total. There are 3718 distinct ceni_site_vote_IDs. 

```{r echo=TRUE}
#rm(list=b)

merge <- read_excel(paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "raw")),'ceni_group_quart.xlsx', sep="/"), col_types='text')
ceni <- read_excel(paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "raw")),'cenischools_clean_v3.xlsx', sep="/"), col_types='text')%>% dplyr::select(c('ceni_site_vote_ID', 'ceni_nom_sv'))

## Bring together all the matched data from village name=school name
for (i in 1:5){
 temp <- read_excel(paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "raw")),paste('matching_village_school_adm', i, '_goodmatches.xlsx', sep=""), sep="/"), col_types='text')  %>% dplyr::select(c('ceni_site_vote_ID', 'ceni_nom_sv', 'longitude', 'latitude', 'GPS_latitude', 'GPS_longitude', 'NomEcole')) %>% left_join(merge, by=c('ceni_site_vote_ID')) %>% dplyr::select(c('ceni_site_vote_ID','province', 'circonscription', 'ceni_sect_chef_comm', 'ceni_group_quart', 'ceni_address_vill_avenue', 'ceni_nom_sv', 'longitude', 'latitude', 'GPS_latitude', 'GPS_longitude', 'NomEcole')) %>% mutate(source = paste('admvar', i, sep=""))
 
 assign(paste('df', i, sep=""), temp)
 
}

## Bring together all the matched data from Kinshasa, big cities, and small localities matching
df_list <- c('_bigcities_15km.xlsx', '_kinshasa.xlsx', '_small.xlsx')

for (c in df_list){
  temp <- read_excel(paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")), paste('georeference', c, sep=""), sep="/"), col_types='text') %>% dplyr::select(c('ceni_site_vote_ID', 'ceni_nom_sv', 'longitude', 'latitude','source')) %>% left_join(merge, by=c('ceni_site_vote_ID')) %>% dplyr::select(c('ceni_site_vote_ID','province', 'circonscription', 'ceni_sect_chef_comm', 'ceni_group_quart', 'ceni_address_vill_avenue', 'ceni_nom_sv', 'longitude', 'latitude', 'source'))
  
  assign(paste('df', which(df_list == c)+5, sep=''), temp)
  rm(temp)
}


## Import Google API coordinates
df9 <- read_csv(paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "raw")),'Votingsites_DRC_GglAPI.csv', sep="/"), col_types = cols(ceni_site_vote_ID = col_character())) %>% left_join(merge, by=c('ceni_site_vote_ID'))  %>% dplyr::select(c('ceni_site_vote_ID','province', 'circonscription', 'ceni_sect_chef_comm', 'ceni_group_quart', 'ceni_address_vill_avenue', 'longitude', 'latitude')) %>% mutate(source = 'api')

df_village_school <- bind_rows(df1, df2, df3, df4, df5) 
df_temp1 <- rbind_dfs(df_village_school, df6)
df_temp2 <- rbind_dfs(df_temp1, df7)
df_final <- rbind_dfs(df_temp2, df8)

`%notin%` <- Negate(`%in%`)
# Add Google API coordinates if the ceni_site_vote_ID doesn't already exist in the data
df10 <- dplyr::filter(df9, ceni_site_vote_ID %notin% df_final$ceni_site_vote_ID )

# Bring all the data points together and remove duplicates by ceni_site_vote_ID, ceni_nom_sv, and latitude.
df_all <- rbind_dfs(df_final, df10, clearRowNames = TRUE) %>% dplyr::filter(!is.na(longitude)) %>% dplyr::mutate(ceni_nom_sv = gsub("[[:blank:]]", "",ceni_nom_sv)) %>% dplyr::mutate(identifier = paste(ceni_site_vote_ID, ceni_nom_sv, latitude)) %>% dplyr::mutate(identifier = gsub("[[:blank:]]", "",identifier))


df_all$longitude <- as.numeric(df_all$longitude)
df_all$latitude <- as.numeric(df_all$latitude)

df_all <- df_all  %>% dplyr::filter(!is.na(latitude)) %>% dplyr::distinct(identifier, .keep_all=TRUE)

# Export the data
write_xlsx(df_all,paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'df_georef_all.xlsx', sep="/"))


```


## Create buffer and add schools

For each admin unit, I'm performing incremental buffering. I take all the schools matched and take the average of coordinates and then create buffers of different km. For the km information, see the excel file names in write_xlsx parts.

### 1. First buffer

The first buffer is created for province, circonscription, ceni_sect_chef_comm, ceni_group_quart, ceni_address_vill_avenue. For all of the buffers in the first admin variable, there is no increase in the georeferenced school numbers.

```{r eval=FALSE, include=FALSE}
rm(list=b)
`%notin%` <- Negate(`%in%`)
# This is where I change the xlsx file name as I add schools by different buffers incrementally:
df_all <- read_excel(paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'matching_buffers1_5km.xlsx', sep="/"), col_types='text')
# If there are any duplicates by ceni_site_vote_ID, ceni_nom_sv, and latitude remove them:
matching_adm1 <- df_all %>% dplyr::mutate(ceni_nom_sv = gsub("[[:blank:]]", "",ceni_nom_sv)) %>% dplyr::mutate(admvar = paste(province, circonscription, ceni_sect_chef_comm, ceni_group_quart, ceni_address_vill_avenue)) %>% dplyr::mutate(school = ceni_nom_sv) %>% dplyr::mutate(NomEcole = gsub("[[:blank:]]", "", NomEcole)) %>% dplyr::mutate(admvar = gsub("[[:blank:]]", "", admvar)) %>% dplyr::mutate(identifier = paste(ceni_site_vote_ID, ceni_nom_sv, latitude)) %>% dplyr::mutate(identifier = gsub("[[:blank:]]", "",identifier)) %>% dplyr::distinct(identifier, .keep_all=TRUE)

matching_adm1$longitude <- as.numeric(matching_adm1$longitude)
matching_adm1$latitude <- as.numeric(matching_adm1$latitude)

# Take the means of latitude and longitude for each admin unit group:
temp1 <- matching_adm1  %>% group_by(admvar) %>% dplyr::summarise(across(c("latitude", "longitude"), ~ mean(.x, na.rm = TRUE)))

ceni <- read_excel(paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "raw")),'cenischools_clean_v3.xlsx', sep="/")) %>% dplyr::mutate(ceni_nom_sv = gsub("[[:blank:]]", "",ceni_nom_sv)) %>% dplyr::mutate(admvar = paste(province, circonscription, ceni_sect_chef_comm, ceni_group_quart, ceni_address_vill_avenue)) %>% dplyr::mutate(school = ceni_nom_sv)%>% dplyr::mutate(admvar = gsub("[[:blank:]]", "", admvar))
  
sige <- sigeschools.all %>% dplyr::mutate(NomEcole = gsub("[[:blank:]]", "", NomEcole)) %>% dplyr::mutate(school = NomEcole) %>% dplyr::filter(NomEcole %notin% matching_adm1$NomEcole)

sige$longitude <- as.numeric(sige$longitude)
sige$latitude <- as.numeric(sige$latitude)

coordinates_sf = st_as_sf(sige, coords = c("GPS_longitude", "GPS_latitude"), 
                                    crs = 4326)

  

small_villes <-  unique(temp1$admvar)

for(s in small_villes) {
  
  temp <- temp1 %>% dplyr::filter(admvar == s)
  temp_admin <- matching_adm1 %>% dplyr::filter(admvar == s)
  
  # Make sure you keep the CENI schools which are not already georeferenced: 
  
  temp_ceni <- ceni %>% dplyr::filter(ceni_nom_sv %notin% df_all$ceni_nom_sv) %>% dplyr::filter(admvar == s)

  temp_sf = st_as_sf(temp, coords = c("longitude", "latitude"), 
                                    crs = 4326)
  # Create buffer around the mean coordinates:
  temp_buffer <- st_buffer(temp_sf, 3000)
  
  admin <- st_join(coordinates_sf,  temp_buffer, left=FALSE) 
  # Merge data by the school name
  matching <- left_join(temp_ceni,admin, by = "school")
  matching_f <- rbind_dfs(temp_admin, matching, clearRowNames = TRUE)
  assign(s, matching)
  
} 

a = ls()
index = which(a %in% small_villes)
b = a[index]

matching_binded1 <- do.call(bind_rows, lapply(b, get, env=environment()))
matching_binded1 <- matching_binded1 %>% dplyr::mutate(source = "adm1_3km")
matching_adm1$ceni_site_vote_ID <- as.numeric(matching_adm1$ceni_site_vote_ID)
matching_final1 <- dplyr::bind_rows(matching_adm1, matching_binded1)


test <- matching_final1  %>% dplyr::filter(!is.na(latitude)) %>% dplyr::mutate(identifier = paste(ceni_site_vote_ID, ceni_nom_sv, latitude)) %>% dplyr::mutate(identifier = gsub("[[:blank:]]", "",identifier)) %>% dplyr::distinct(identifier, .keep_all=TRUE)

test<- test[, 1:15]

#write_xlsx(test,paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'matching_buffers1_3km.xlsx', sep="/"))
#write_xlsx(test,paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'matching_buffers1_5km.xlsx', sep="/"))
write_xlsx(test,paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'matching_buffers1_8km.xlsx', sep="/"))
```


### 2. Second buffer

The second buffer is created for province, circonscription, ceni_sect_chef_comm, ceni_group_quart. To begin with there are 4121 observations, and the number of observations for each buffer is as follows:

  * Initial:        3756
  * 5 km buffer:    4137
  * 8 km buffer:    4398
  * 10 km buffer:   4562

```{r eval=FALSE, include=FALSE}
rm(list=b)
`%notin%` <- Negate(`%in%`)
df <- read_excel(paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'matching_buffers2_8km.xlsx',sep="/"), col_types="text")
df[,8:11] <- lapply(df[,8:11], as.numeric)
df$ceni_site_vote_ID <- as.numeric(df$ceni_site_vote_ID)
matching_adm1 <- df %>% dplyr::mutate(ceni_nom_sv = gsub("[[:blank:]]", "",ceni_nom_sv)) %>% dplyr::mutate(admvar = paste(province, circonscription, ceni_sect_chef_comm, ceni_group_quart)) %>% dplyr::mutate(school = ceni_nom_sv) %>% dplyr::mutate(NomEcole = gsub("[[:blank:]]", "", NomEcole)) %>% dplyr::mutate(admvar = gsub("[[:blank:]]", "", admvar)) %>% dplyr::mutate(identifier = gsub("[[:blank:]]", "",identifier)) %>% dplyr::distinct(identifier, .keep_all=TRUE)

matching_adm1$longitude <- as.numeric(matching_adm1$longitude)
matching_adm1$latitude <- as.numeric(matching_adm1$latitude)

temp1 <- matching_adm1  %>% group_by(admvar) %>% dplyr::summarise(across(c("latitude", "longitude"), ~ mean(.x, na.rm = TRUE)))

ceni <- read_excel(paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "raw")),'cenischools_clean_v3.xlsx', sep="/")) %>% dplyr::mutate(ceni_nom_sv = gsub("[[:blank:]]", "",ceni_nom_sv)) %>% dplyr::mutate(admvar = paste(province, circonscription, ceni_sect_chef_comm, ceni_group_quart)) %>% dplyr::mutate(school = ceni_nom_sv)%>% dplyr::mutate(admvar = gsub("[[:blank:]]", "", admvar))
  
sige <- sigeschools.all %>% dplyr::mutate(NomEcole = gsub("[[:blank:]]", "", NomEcole)) %>% dplyr::mutate(school = NomEcole) %>% dplyr::filter(NomEcole %notin% matching_adm1$NomEcole)

sige$longitude <- as.numeric(sige$longitude)
sige$latitude <- as.numeric(sige$latitude)

coordinates_sf = st_as_sf(sige, coords = c("GPS_longitude", "GPS_latitude"), 
                                    crs = 4326)

  

small_villes <-  unique(temp1$admvar)

for(s in small_villes) {
  
  temp <- temp1 %>% dplyr::filter(admvar == s)
  
  temp_admin <- matching_adm1 %>% dplyr::filter(admvar == s)
  
  temp_ceni <- ceni %>% dplyr::filter(admvar == s) %>% dplyr::filter(ceni_nom_sv %notin% df$ceni_nom_sv)

     

  temp_sf = st_as_sf(temp, coords = c("longitude", "latitude"), 
                                    crs = 4326)
    
  temp_buffer <- st_buffer(temp_sf,10000)
  

  admin <- st_join(coordinates_sf,  temp_buffer, left=FALSE) 
  
  
  matching <- left_join(temp_ceni,admin, by = "school")
  matching_f <- rbind_dfs(temp_admin, matching, clearRowNames = TRUE)
  assign(s, matching)
  
} 

a = ls()
#index = which(str_detect(a, "[[:upper:]]|Â"))
index = which(a %in% small_villes)
b = a[index]

matching_binded1 <- do.call(bind_rows, lapply(b, get, env=environment()))
matching_binded1 <- matching_binded1 %>% dplyr::mutate(source = "adm2_10km")
matching_adm1$ceni_site_vote_ID <- as.numeric(matching_adm1$ceni_site_vote_ID)
matching_final1 <- dplyr::bind_rows(matching_adm1, matching_binded1)

test <- matching_final1  %>% dplyr::filter(!is.na(latitude)) %>% dplyr::mutate(identifier = paste(ceni_site_vote_ID, ceni_nom_sv, latitude)) %>% dplyr::mutate(identifier = gsub("[[:blank:]]", "",identifier)) %>% dplyr::distinct(identifier, .keep_all=TRUE)

test<- test[, 1:15]

#write_xlsx(test,paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'matching_buffers2_5km.xlsx', sep="/"))
#write_xlsx(test,paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'matching_buffers2_8km.xlsx', sep="/"))
write_xlsx(test,paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'matching_buffers2_10km.xlsx', sep="/"))

```


### 3. Third buffer

The third buffer is created for province, circonscription, ceni_sect_chef_comm.The final number of observations for each buffer is as follows:

  * Initial:        4562
  * 8 km buffer:    4949
  * 20 km buffer:   6160
  * 30 km buffer:   7125

```{r eval=FALSE, include=FALSE}
rm(list=b)
`%notin%` <- Negate(`%in%`)
df <- read_excel(paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'matching_buffers3_20km.xlsx',sep="/"), col_types="text")
df[,8:11] <- lapply(df[,8:11], as.numeric)
df$ceni_site_vote_ID <- as.numeric(df$ceni_site_vote_ID)
matching_adm1 <- df %>% dplyr::mutate(ceni_nom_sv = gsub("[[:blank:]]", "",ceni_nom_sv)) %>% dplyr::mutate(admvar = paste(province, circonscription, ceni_sect_chef_comm)) %>% dplyr::mutate(school = ceni_nom_sv) %>% dplyr::mutate(NomEcole = gsub("[[:blank:]]", "", NomEcole)) %>% dplyr::mutate(admvar = gsub("[[:blank:]]", "", admvar)) %>% dplyr::mutate(identifier = gsub("[[:blank:]]", "",identifier)) %>% dplyr::distinct(identifier, .keep_all=TRUE)

matching_adm1$longitude <- as.numeric(matching_adm1$longitude)
matching_adm1$latitude <- as.numeric(matching_adm1$latitude)

temp1 <- matching_adm1  %>% group_by(admvar) %>% dplyr::summarise(across(c("latitude", "longitude"), ~ mean(.x, na.rm = TRUE)))

ceni <-read_excel(paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "raw")),'cenischools_clean_v3.xlsx', sep="/")) %>% dplyr::mutate(ceni_nom_sv = gsub("[[:blank:]]", "",ceni_nom_sv)) %>% dplyr::mutate(admvar = paste(province, circonscription, ceni_sect_chef_comm)) %>% dplyr::mutate(school = ceni_nom_sv)%>% dplyr::mutate(admvar = gsub("[[:blank:]]", "", admvar))
  
sige <- sigeschools.all %>% dplyr::mutate(NomEcole = gsub("[[:blank:]]", "", NomEcole)) %>% dplyr::mutate(school = NomEcole) %>% dplyr::filter(NomEcole %notin% matching_adm1$NomEcole)

sige$longitude <- as.numeric(sige$longitude)
sige$latitude <- as.numeric(sige$latitude)

coordinates_sf = st_as_sf(sige, coords = c("GPS_longitude", "GPS_latitude"), 
                                    crs = 4326)

  

small_villes <-  unique(temp1$admvar)

for(s in small_villes) {
  
  temp <- temp1 %>% dplyr::filter(admvar == s)
  
  temp_admin <- matching_adm1 %>% dplyr::filter(admvar == s)
  
  temp_ceni <- ceni %>% dplyr::filter(admvar == s) %>% dplyr::filter(ceni_nom_sv %notin% df$ceni_nom_sv)

     

  temp_sf = st_as_sf(temp, coords = c("longitude", "latitude"), 
                                    crs = 4326)
    
  temp_buffer <- st_buffer(temp_sf, 30000)
  

  admin <- st_join(coordinates_sf,  temp_buffer, left=FALSE) 
  
  
  matching <- left_join(temp_ceni,admin, by = "school")
  matching_f <- rbind_dfs(temp_admin, matching, clearRowNames = TRUE)
  assign(s, matching)
  
} 

a = ls()
index = which(a %in% small_villes)
b = a[index]

matching_binded1 <- do.call(bind_rows, lapply(b, get, env=environment()))
matching_binded1 <- matching_binded1 %>% dplyr::mutate(source = "adm3_20km")
matching_adm1$ceni_site_vote_ID <- as.numeric(matching_adm1$ceni_site_vote_ID)
matching_final1 <- dplyr::bind_rows(matching_adm1, matching_binded1)

test <- matching_final1  %>% dplyr::filter(!is.na(latitude)) %>% dplyr::mutate(identifier = paste(ceni_site_vote_ID, ceni_nom_sv, latitude)) %>% dplyr::mutate(identifier = gsub("[[:blank:]]", "",identifier)) %>% dplyr::distinct(identifier, .keep_all=TRUE)

test<- test[, 1:15]

#write_xlsx(test,paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'matching_buffers3_8km.xlsx', sep="/"))
#write_xlsx(test,paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'matching_buffers3_20km.xlsx', sep="/"))
write_xlsx(test,paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'matching_buffers3_30km.xlsx', sep="/"))
```


### 4. Fourth buffer

The fourth buffer is created for province, circonscription. The final number of observations for each buffer is as follows:

  * Initial:        7125
  * 20 km buffer:   7420
  * 25 km buffer:   7609
  * 30 km buffer:   7786
  * 35 km buffer:   7965
  * 40 km buffer:   8154
  * 45 km buffer:   8404
  * 50 km buffer:   8630

```{r echo=TRUE}
#rm(list=b)
`%notin%` <- Negate(`%in%`)
df <- read_excel(paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'matching_buffers4_45km.xlsx',sep="/"), col_types="text")
df[,8:11] <- lapply(df[,8:11], as.numeric)
df$ceni_site_vote_ID <- as.numeric(df$ceni_site_vote_ID)
matching_adm1 <- df %>% dplyr::mutate(ceni_nom_sv = gsub("[[:blank:]]", "",ceni_nom_sv)) %>% dplyr::mutate(admvar = paste(province, circonscription)) %>% dplyr::mutate(school = ceni_nom_sv) %>% dplyr::mutate(NomEcole = gsub("[[:blank:]]", "", NomEcole)) %>% dplyr::mutate(admvar = gsub("[[:blank:]]", "", admvar))  %>% dplyr::mutate(identifier = gsub("[[:blank:]]", "",identifier)) %>% dplyr::distinct(identifier, .keep_all=TRUE)

matching_adm1$longitude <- as.numeric(matching_adm1$longitude)
matching_adm1$latitude <- as.numeric(matching_adm1$latitude)


temp1 <- matching_adm1  %>% group_by(admvar) %>% dplyr::summarise(across(c("latitude", "longitude"), ~ mean(.x, na.rm = TRUE)))

ceni <- read_excel(paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "raw")),'cenischools_clean_v3.xlsx', sep="/")) %>% dplyr::mutate(ceni_nom_sv = gsub("[[:blank:]]", "",ceni_nom_sv)) %>% dplyr::mutate(admvar = paste(province, circonscription)) %>% dplyr::mutate(school = ceni_nom_sv)%>% dplyr::mutate(admvar = gsub("[[:blank:]]", "", admvar))
  
sige <- sigeschools.all %>% dplyr::mutate(NomEcole = gsub("[[:blank:]]", "", NomEcole)) %>% dplyr::mutate(school = NomEcole) %>% dplyr::filter(NomEcole %notin% matching_adm1$NomEcole)

sige$longitude <- as.numeric(sige$longitude)
sige$latitude <- as.numeric(sige$latitude)

coordinates_sf = st_as_sf(sige, coords = c("GPS_longitude", "GPS_latitude"), 
                                    crs = 4326)

  

small_villes <-  unique(temp1$admvar)

for(s in small_villes) {
  
  temp <- temp1 %>% dplyr::filter(admvar == s)
  
  temp_admin <- matching_adm1 %>% dplyr::filter(admvar == s)
  
  temp_ceni <- ceni %>% dplyr::filter(admvar == s) %>% dplyr::filter(ceni_nom_sv %notin% df$ceni_nom_sv)

     

  temp_sf = st_as_sf(temp, coords = c("longitude", "latitude"), 
                                    crs = 4326)
    
  temp_buffer <- st_buffer(temp_sf, 50000)
  

  admin <- st_join(coordinates_sf,  temp_buffer, left=FALSE) 
  
  
  matching <- left_join(temp_ceni,admin, by = "school")
  matching_f <- rbind_dfs(temp_admin, matching, clearRowNames = TRUE)
  assign(s, matching)
  
} 

a = ls()
#index = which(str_detect(a, "[[:upper:]]|Â"))
index = which(a %in% small_villes)
b = a[index]


matching_binded1 <- do.call(bind_rows, lapply(b, get, env=environment()))
matching_binded1 <- matching_binded1 %>% dplyr::mutate(source = "adm4_50km")
matching_adm1$ceni_site_vote_ID <- as.numeric(matching_adm1$ceni_site_vote_ID)
matching_final1 <- dplyr::bind_rows(matching_adm1, matching_binded1)

test <- matching_final1  %>% dplyr::filter(!is.na(latitude)) %>% dplyr::mutate(identifier = paste(ceni_site_vote_ID, ceni_nom_sv, latitude)) %>% dplyr::mutate(identifier = gsub("[[:blank:]]", "",identifier)) %>% dplyr::distinct(identifier, .keep_all=TRUE)

test<- test[, 1:15]

#write_xlsx(test,paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'matching_buffers4_20km.xlsx', sep="/"))
#write_xlsx(test,paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'matching_buffers4_25km.xlsx', sep="/"))
#write_xlsx(test,paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'matching_buffers4_30km.xlsx', sep="/"))
#write_xlsx(test,paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'matching_buffers4_35km.xlsx', sep="/"))
#write_xlsx(test,paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'matching_buffers4_40km.xlsx', sep="/"))
#write_xlsx(test,paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'matching_buffers4_45km.xlsx', sep="/"))
write_xlsx(test,paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'matching_buffers4_50km.xlsx', sep="/"))

uniques <- unique(test$ceni_site_vote_ID)

rm(list=b)
```

I'm keeping the code chunk above to show the process, the same code was run for other admin units with varying buffers.

In the code below, I'm merging the final georeference data with the ceni dataset by ceni_site_vote_ID:

```{r echo=TRUE, message=FALSE, warning=FALSE}
df <- read_excel(paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'matching_buffers4_50km.xlsx',sep="/")) %>% dplyr::distinct(ceni_site_vote_ID, .keep_all=TRUE) %>% dplyr::select(c('ceni_site_vote_ID', 'ceni_nom_sv', 'latitude', 'longitude', 'source'))
ceni_raw <- read_csv(paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "raw")),'ceni_election_2022_05_18.csv',sep="/")) %>% dplyr::rename(ceni_nom_sv_original = ceni_nom_sv)

final <- merge(df, ceni_raw, by="ceni_site_vote_ID", all=TRUE) %>% dplyr::mutate(georeferenced = ifelse(is.na(latitude), "unmatched", "matched"), .after='ceni_nom_sv')

write_xlsx(final,paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'georeference.xlsx', sep="/"))


```

### Statistics

#### 1. Comparison Table

Below are the basic distribution of matched/unmatched observations by the output of interest.
```{r warning=FALSE, message=FALSE}
df <- read_excel(paste((file.path(here::here(current_path) %>% dirname() %>% dirname(), "output")),'georeference.xlsx',sep="/")) 



df2 <- df %>% mutate_if(is.numeric, ~replace_na(., 0)) %>% group_by(georeferenced) %>%
  dplyr::summarise(across(c(bv_prevus, bv_traites, electeurs_attendus, votants, Tshisekedi, Fayulu, Shadary), sum),
                   .groups='drop') %>%
  as.data.frame() %>%
  mutate(votants_to_inscrits = votants/electeurs_attendus) %>%  
  mutate(share_Tshisekedi = Tshisekedi / votants*100) %>%
  mutate(share_Fayulu = Fayulu / votants*100) %>%
  mutate(share_Shadary = Shadary / votants*100)
    

tbl <- knitr::kable(df2[, 1:12], "latex", booktabs = T, caption = "Comparison of Matched and Unmatched Obs by Output of Interest") %>%  kableExtra::kable_styling(latex_options = c("scale_down", "striped", "hold_position")) # will fit table
tbl




```

\newpage

#### 2. Distribution Graphs

```{r out.width = "50%", include=TRUE, echo=FALSE, fig.pos='h', fig.align='center'}
# Distribution of ballot boxes planned
p1 <- df %>%
  mutate(text = fct_reorder(georeferenced, bv_prevus)) %>%
  ggplot( aes(x=bv_prevus, color=text, fill=text)) +
    geom_histogram(alpha=0.6, binwidth = 3) +
    #theme_ipsum() +
    theme(legend.position="none", panel.spacing = unit(1, "lines"), strip.text.x = element_text(size = 8),panel.grid.major.x = element_blank()) +
    xlab("") +
    ylab("Count") +
    facet_wrap(~text) +
  ggtitle("Distribution of Ballot Boxed Planned")
p1

# Distribution of ballot boxes counted

p2 <- df %>%
  mutate(text = fct_reorder(georeferenced, bv_traites)) %>%
  ggplot( aes(x=bv_traites, color=text, fill=text)) +
    geom_histogram(alpha=0.6, binwidth = 3) +
    #theme_ipsum() +
    theme(
      legend.position="none",
      panel.spacing = unit(1, "lines"),
      strip.text.x = element_text(size = 8),
      panel.grid.major.x = element_blank()
    ) +
    xlab("") +
    ylab("Count") +
    facet_wrap(~text) +
  ggtitle("Distribution of Ballot Boxed Counted")
p2


## Distribution of expected voters
p3 <- df %>%
  mutate(text = fct_reorder(georeferenced, electeurs_attendus)) %>%
  ggplot( aes(x=electeurs_attendus, color=text, fill=text)) +
    geom_histogram(alpha=0.6, binwidth = 3) +
    #theme_ipsum() +
    theme(
      legend.position="none",
      panel.spacing = unit(1, "lines"),
      strip.text.x = element_text(size = 8),
      panel.grid.major.x = element_blank()
    ) +
    xlab("") +
    ylab("Count") +
    facet_wrap(~text) +
  ggtitle("Distribution of Expected Voters")
p3


## Distribution of number of voters
p4 <- df %>%
  mutate(text = fct_reorder(georeferenced, votants)) %>%
  ggplot( aes(x=votants, color=text, fill=text)) +
    geom_histogram(alpha=0.6, binwidth = 3) +
    #theme_ipsum() +
    theme(
      legend.position="none",
      panel.spacing = unit(1, "lines"),
      strip.text.x = element_text(size = 8),
      panel.grid.major.x = element_blank()
    ) +
    xlab("") +
    ylab("Count") +
    facet_wrap(~text) +
  ggtitle("Distribution of Number of Voters")
p4


#Among the smallest adm unit, fo how many we have absolutely no georeferenced schools

df3 <- df %>% dplyr::mutate(admvar = paste(province, circonscription, ceni_sect_chef_comm, ceni_group_quart, ceni_address_vill_avenue)) %>%
  group_by(admvar) %>% dplyr::summarise(total = n(), .groups='drop') %>% arrange(admvar)

df4 <- df %>% dplyr::mutate(admvar = paste(province, circonscription, ceni_sect_chef_comm, ceni_group_quart, ceni_address_vill_avenue)) %>%
  group_by(admvar, georeferenced) %>% dplyr::summarise(count = n(), .groups='drop') %>% arrange(admvar) %>% pivot_wider(names_from = georeferenced, values_from = count)

df5 <- merge(df3, df4, by='admvar', all=TRUE) %>% mutate_if(is.numeric, ~replace_na(., 0)) %>% dplyr::mutate(share_unmatched = unmatched/total*100) %>% dplyr::mutate(share_matched = matched/total*100) %>% pivot_longer(cols=c('share_matched', 'share_unmatched'), names_to='group', values_to='shares' )


p5 <- df5 %>%
  dplyr::mutate(text = fct_reorder(group, shares)) %>%
  ggplot( aes(x=shares, color=text, fill=text)) +
    geom_histogram(alpha=0.6, binwidth = 3) +
    #theme_ipsum() +
    theme(
      legend.position="none",
      panel.spacing = unit(1, "lines"),
      strip.text.x = element_text(size = 8),
      panel.grid.major.x = element_blank()
    ) +
    xlab("") +
    ylab("Count") +
    facet_wrap(~text) +
  ggtitle("Distribution of Matching Share on Smallest AdmUnit")
p5


# Count the number of strings

p6 <- df %>%
  mutate(characters = nchar(ceni_nom_sv_original)) %>%
  mutate(text = fct_reorder(georeferenced, characters)) %>%
  ggplot( aes(x=characters, color=text, fill=text)) +
    geom_histogram(alpha=0.6, binwidth = 3) +
    #theme_ipsum() +
    theme(
      legend.position="none",
      panel.spacing = unit(1, "lines"),
      strip.text.x = element_text(size = 8),
      panel.grid.major.x = element_blank()
    ) +
    xlab("") +
    ylab("Count") +
    facet_wrap(~text) +
  ggtitle("Distribution of String Characters in the Original Voting Station")
p6

# Successful georeferencing rate by province

df_total <- df %>% dplyr::mutate(admvar = paste(province)) %>%
  group_by(admvar) %>% dplyr::summarise(total = n(), .groups='drop') %>% arrange(admvar)

df_province <- df %>% dplyr::mutate(admvar = paste(province)) %>%
  group_by(admvar, georeferenced) %>% dplyr::summarise(count = n(), .groups='drop') %>% arrange(admvar) %>% pivot_wider(names_from = georeferenced, values_from = count)

df5 <- merge(df_total, df_province, by='admvar', all=TRUE) %>% mutate_if(is.numeric, ~replace_na(., 0)) %>% dplyr::mutate(share_unmatched = unmatched/total*100) %>% dplyr::mutate(share_matched = matched/total*100) %>% pivot_longer(cols=c('share_matched', 'share_unmatched'), names_to='group', values_to='shares' )

plt <- df5 %>% dplyr::filter(group %in% c('share_matched')) %>% arrange(shares) 

p <- barplot(height=plt$shares, names.arg=plt$admvar, las=2, cex.names=0.6, col="cornflowerblue", ylim=c(0,100), main="Matching Performance by Province (Percent)")

```


#### 3. Distances

Next, I'm taking the smallest admin unit (i.e. province, circonscription, ceni_sect_chef_comm, ceni_group_quart, ceni_address_vill_avenue) and for the regions where there is more than one school matched, I'm creating the statistics for the distances (min, max, mean, sd). Additionally, the count column gives the number of georeferenced schools in the respective admin unit.

```{r echo=FALSE, message=FALSE, warning=FALSE}
options(scipen = 999)
matching <- df %>% dplyr::filter(georeferenced == "matched") %>% dplyr::mutate(town_province1 = paste(province, circonscription, ceni_sect_chef_comm, ceni_group_quart, ceni_address_vill_avenue)) %>%  dplyr::mutate(town_province1 = gsub("[[:blank:]]", "", town_province1)) %>% group_by(town_province1) %>% add_count(name = "number" )  %>% dplyr::filter(number > 1) %>%  dplyr::mutate(match_var = ceni_nom_sv)

territoire <-  unique(matching$town_province1) 

for(t in territoire) {
temp_matching <- matching %>% dplyr::filter(town_province1 == t) %>%  dplyr::select(c('ceni_site_vote_ID','province', 'circonscription', 'ceni_sect_chef_comm', 'ceni_group_quart', 'ceni_address_vill_avenue', 'ceni_nom_sv', 'town_province1','longitude', 'latitude', 'match_var'))
temp_sf <- st_as_sf(temp_matching, coords = c("longitude", "latitude"), 
                                    crs = 4326)
my_list <- unique(temp_sf$match_var)
for(i in 1:length(my_list)){
lead <- temp_sf %>% dplyr::mutate(lead = geometry[row_number() + i])
dist <- lead %>% dplyr::mutate(dist = st_distance(geometry, lead, by_element = T))
dist_df <- as.data.frame(dist$dist)
dist_df <- lapply(dist_df,as.numeric)
lead_df <- as.data.frame(lead$lead)
match_var_2 <- temp_sf %>% dplyr::mutate(match_var_2 = match_var[row_number() + i])
match_var_2 <- as.data.frame(match_var_2$match_var_2)
temp_sf[paste0("lead", i-1)] <- lead_df
temp_sf[paste0("dist", i-1)] <- dist_df
temp_sf[paste0("match_var_", i-1)] <- match_var_2
dataframe <- temp_sf
new_rows <- dataframe[ , grepl( "dist" , names(dataframe) )]
matched <- data.frame(distances = na.omit(unlist(new_rows, use.names= FALSE)))
matched['admvar'] = t
summary <- matched %>% 
  summarise( n = n(),
             mean = mean(distances),
             sd = sd(distances),
             min_dist = min(distances),
             max_dist = max(distances))
summary['admvar'] = t

assign(t, summary)
}
}



a = ls()
index = which(str_detect(a, "[[:upper:]]"))
b = a[index]
distances <- do.call(bind_rows, lapply(b, get, env=environment()))
rm(list = b)

counts <- df4 %>% dplyr::filter(matched > 1) %>% dplyr::mutate(admvar = gsub("[[:blank:]]", "", admvar)) %>% .[, -2]
summary_distances <- merge(counts, distances, by='admvar',  all=TRUE) %>% .[, -3] %>% dplyr::arrange(max_dist)

tbl2 <- knitr::kable(summary_distances, "latex", booktabs = T, longtable=TRUE, caption = "Summary Statistics of Distances") %>%  kableExtra::kable_styling(latex_options = c("scale_down", "striped", "hold_position", "repeat_header"), font_size = 7)  %>% # will fit table
  landscape()
tbl2


p8 <- summary_distances %>%
  ggplot( aes(x=mean, fill="skyblue3")) +
    geom_histogram(alpha=1, binwidth =100) +
    #theme_ipsum() +
    theme(
      legend.position="none",
      panel.spacing = unit(1, "lines"),
      strip.text.x = element_text(size = 8),
      panel.grid.major.x = element_blank()
    ) +
    xlab("") +
    ylab("Count") +
  ggtitle("Distribution of Mean Distances in Smallest Admin Units")
p8
```
I'm putting some admin units where the results seem off:

```{r}
names <- c("TSHOPOISANGIBOLOMBOKINAYAHISULI", "KASAILUEBOLUEBO-KABAMBAIENAWETUMANDE", "KWANGOKASONGO-LUNDAKIBUNDANAKASANZA", "KWANGOKASONGO-LUNDAKIBUNDANAKASANZA" )
testdf <- df %>% dplyr::filter(georeferenced == "matched") %>% dplyr::mutate(town_province1 = paste(province, circonscription, ceni_sect_chef_comm, ceni_group_quart, ceni_address_vill_avenue)) %>%  dplyr::mutate(town_province1 = gsub("[[:blank:]]", "", town_province1)) %>% dplyr::filter(town_province1 %in% names) %>% dplyr::select('ceni_site_vote_ID', 'ceni_nom_sv', 'georeferenced', 'latitude', 'longitude', 'town_province1') %>% dplyr::rename(admvar = town_province1)

tbl3 <- knitr::kable(testdf, "latex", booktabs = T, caption = "Example") %>%  kableExtra::kable_styling(latex_options = c("scale_down", "striped", "hold_position")) 
tbl3
```
There seem to be some schools with same school name but different voting station ID, so when creating buffers since I do matching only on the school name, the same coordinates are matched with those schools.

